Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-07-07 outputs/paper/paper.qmd
Updates to paper

pollution %>% filter(pollutant == "CO") %>% ggplot(
  aes(x = month_name, y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppm)")

>>>>

pollution %>% filter(pollutant == "CO") %>% ggplot(
  aes(x = factor(month_name, level = level_order), y = mean_pollution, color = pollutant)) + geom_point() + 
  labs(color="Pollutant") + xlab("Month") + ylab("Mean Pollution (ppm)")
